A systematic search for transiting planets in the \KT\ data

### 2015-02-14 ms.tex
updated EB table and discussion

The photometry from the \KT\ extension of NASA's \kepler\ mission is
afflicted by systematic effects caused by the relative imprecision of the
telescope pointing and other spacecraft issues.
We present a method for searching these light curves for evidence of
exoplanets by simultaneously fitting for these systematics and the
transit signals of interest.
This method is more computationally expensive than standard search algorithms
but we demonstrate that it can be efficiently implemented and used to robustly
discover transit signals.
We apply this method to the full Campaign 1 dataset and report a list of XXX
planet candidates transiting YYY stars.
For all planet candidates, we present posterior distributions on the
properties of each system based strictly on the transit observables.
We also present a list of ZZZ candidate eclipsing binary systems.

@@

The \paper\ is organized as follows.
In \sect{phot}, we describe our method of extracting aperture photometry from
the calibrated \KT\ postage stamp time series.
In \sect{model} (with details in \app{math}), we describe our data-driven
model for the systematic trends in the photometric light curves and our method
for fitting this model simultaneously with a transit signal.
In \sect{search}, we give the detailed procedure that we use for discovering
and vetting planet candidates.
To quantify the performance and detection efficiency of our pipeline, we test
(in \sect{perform}) the recovery and false alarm rate of synthetic transit
signals, spanning a large range of physical parameters, injected into real
\KT\ light curves.
Finally, in \sect{results}, we present a catalog of XXXX planet candidates
orbiting WWWW stars---and a supplementary list of YYYY eclipsing binary
candidates---in the publicly available \KT\ Campaign 1 dataset.

@@

The starting point for analysis is the raw pixel data.
We download the full set of \dfmtodo{XXX} target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
We extract photometry using fixed circular apertures of varying sizes
centered on the predicted location of the target star based on the world
coordinate system.
\dfmtodo{In detail, the apertures are only approximately circular; each pixel
gets a weight of unity if its center is in the circle, and zero otherwise.}
For each target, we performed the photometry in a set of
circular apertures ranging in radius from 0.5 to
5 pixels (in steps of 0.5 pixels) and---following
\citet{Vanderburg:2014}---chose the aperture size that resulted in the
smallest CDPP \citep{cdpp}
with a 6 hour window.\footnote{Note that although we chose a specific
aperture for each star, photometry for this aperture and every other
aperture size at which we easured is all available online at
\dfmtodo{some URL}.}

@@

The periodic search procedure returned three signals per target so this gave
an initial list of ZZZZ candidates.
The vast majority of these signals are, of course, not induced by a
transiting planet.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\TIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
found that at this stage, it produced a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
Figure SOMEFIGURE shows the distribution of signal-to-noise for a set of
injections and compares it to the distribution of false candidates that are
proposed by the pipeline.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are very
contaminated by false alarms.
This might be because of the fact that our independence assumption
(SOMEEQUATION) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days.
After these cuts, we're left with 741 candidates that we then examine by hand.
The full list of peaks and their relevant meta data is available online at
\dfmtodo{SOMEURL}.

@@

After our initial cuts on the candidate list, the majority of signals are
still false alarms mostly due to variable stars or single outlying data
points.
It should be possible to construct a more robust machine vetting algorithm
that discards these samples without missing real transits (CITE SOME THINGS)
but for the purposes of this \paper, we simply inspect the light curve for
each of the YYYY candidates \emph{by hand} to discard signals that are not
convincing transits.
The results of this vetting can be seen online at SOMEURL.

This vetting resulted in a list of ZZZZ transiting candidates.
Many of these signals are due to astrophysical ``false positives'' like
eclipsing binaries or blending.
We address this effect in the following section and separate the list of
candidates into a list of astrophysical false positives and planet candidates.

@@

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal variations is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging (cite Howell).

@@

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
in prep?).
Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
SOMECANDIDATE.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (\eqalt{linear-model}), we modeled the light curve as a linear
combination of ELCs and a simple box transit model at a given period, phase,
and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.
Since the motions won't necessarily point in a consistent direction across
transits, we treat each transit independently and report the average offset
amplitude weighted by the precision of each measurement.
To compute the significance of a centroid offset, we bootstrap the offset
amplitude for models at the same period and duration but randomly oriented
phases.
If the centroid measured for the candidate transit is substantially larger
than the random realizations, we label the candidate as a false positive.
In practice, the precision of the centroid measurements isn't sufficient to
robustly reject many candidates but of the list of 100 (RIGHT NUMBER), two
candidates---EPIC AAA and BBB---have offsets large enough that we remove them
from our final catalog.
Figure SOMEFIGURE shows the distribution of centroid offsets across the full
catalog.

@@

After running the 21XXX light curves through our full pipeline, we end up with
XXXX TCEs \dfmtodo{change this name} and after hand vetting by the two first
authors of this \paper, we are left with YYYY convincing transiting
candidates.
We choose to separate this list into two tables: planet candidates
(\tab{cand}) and eclipsing binary candidates (\tab{eb}).
For our purposes, we define an binary candidate as any system where we can
find a secondary eclipse by visual inspection but in most cases, the
secondary eclipse is also detected as a smaller transit signal at the same
period as the primary.
In this dataset, we discover ZZZ planet candidates around WWW stars.
Two of these were previously published \citep{Crossfield:2015} but, to our
knowledge, the remaining list is currently unpublished.
The third planet published by \citet{Crossfield:2015} is found as the third
signal for that target by our pipeline but it falls just below our
signal-to-noise cut so we left it out of the catalog for consistency.
This suggests that a less conservative cut in signal-to-noise and more
aggressive machine vetting could yield a much more complete catalog at smaller
radii and longer periods even with the existing dataset.

For the binaries, we simply list the period, phase, and depth determined by
the search algorithm but for the planet candidates, we perform a full physical
transit fit to the light curve.
To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
sample from the posterior probability for the stellar and planetary
parameters taking limb darkening and integration time into account.
In this fit, we continue to model the trends in the data as a linear
combination of 150 ELCs but, at this point, we combine this with a realistic
light curve model \citet{ma, kipping-ld}.
Even though we have no constraints on the stellar parameters, we also sample
over a large range in stellar mass and radius so that future measurements can
be applied by re-weighting the published samples.
In \tab{cand} we list the sample quantiles for the observable quantities and
the full chains are available electronically at \dfmtodo{some URL}.

@@

\begin{table}[p]
\begin{center}
\include{tab-eb}
\end{center}
\caption{%
Probable binaries.
\tablabel{eb}}
\end{table}

>>>>

The photometry from the \KT\ extension of NASA's \kepler\ mission is
afflicted by systematic effects caused by the relative imprecision of the
telescope pointing and other spacecraft issues.
We present a method for searching these light curves for evidence of
exoplanets by simultaneously fitting for these systematics and the
transit signals of interest.
This method is more computationally expensive than standard search algorithms
but we demonstrate that it can be efficiently implemented and used to robustly
discover transit signals.
We apply this method to the full Campaign 1 dataset and report a list of 38
planet candidates transiting 33 stars.
For all planet candidates, we present posterior distributions on the
properties of each system based strictly on the transit observables.
We also present a list of ZZZ candidate eclipsing binary systems.

@@

The \paper\ is organized as follows.
In \sect{phot}, we describe our method of extracting aperture photometry from
the calibrated \KT\ postage stamp time series.
In \sect{model} (with details in \app{math}), we describe our data-driven
model for the systematic trends in the photometric light curves and our method
for fitting this model simultaneously with a transit signal.
In \sect{search}, we give the detailed procedure that we use for discovering
and vetting planet candidates.
To quantify the performance and detection efficiency of our pipeline, we test
(in \sect{perform}) the recovery and false alarm rate of synthetic transit
signals, spanning a large range of physical parameters, injected into real
\KT\ light curves.
Finally, in \sect{results}, we present a catalog of 38 planet candidates
orbiting 33 stars---and a supplementary list of YYYY eclipsing binary
candidates---in the publicly available \KT\ Campaign 1 dataset.

@@

The starting point for analysis is the raw pixel data.
We download the full set of 21,703 target pixel files for \KT's Campaign 1
from MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
We extract photometry using fixed circular apertures of varying sizes
centered on the predicted location of the target star based on the world
coordinate system.
\dfmtodo{In detail, the apertures are only approximately circular; each pixel
gets a weight of unity if its center is in the circle, and zero otherwise.}
For each target, we performed the photometry in a set of
circular apertures ranging in radius from 0.5 to
5 pixels (in steps of 0.5 pixels) and---following
\citet{Vanderburg:2014}---chose the aperture size that resulted in the
smallest CDPP \citep{cdpp}
with a 6 hour window.\footnote{Note that although we chose a specific
aperture for each star, photometry for this aperture and every other
aperture size at which we easured is all available online at
\dfmtodo{some URL}.}

@@

The periodic search procedure returned three signals per target so this gave
an initial list of 65,109 candidates.
The vast majority of these signals are, of course, not induced by a
transiting planet.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\TIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
found that at this stage, it produced a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
Figure SOMEFIGURE shows the distribution of signal-to-noise for a set of
injections and compares it to the distribution of false candidates that are
proposed by the pipeline.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are very
contaminated by false alarms.
This might be because of the fact that our independence assumption
(SOMEEQUATION) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days.
After these cuts, we're left with 741 candidates that we then examine by hand.
The full list of peaks and their relevant meta data is available online at
\dfmtodo{SOMEURL}.

@@

After our initial cuts on the candidate list, the majority of signals are
still false alarms mostly due to variable stars or single outlying data
points.
It should be possible to construct a more robust machine vetting algorithm
that discards these samples without missing real transits (CITE SOME THINGS)
but for the purposes of this \paper, we simply inspect the light curve for
each of the 741 candidates \emph{by hand} to discard signals that are not
convincing transits.
The results of this vetting can be seen online at SOMEURL.

This vetting resulted in a list of 101 candidate transit signals.
Many of these signals are due to astrophysical ``false positives'' like
eclipsing binaries or blending.
We address this effect in the following section and separate the list of
candidates into a list of astrophysical false positives and planet candidates.

@@

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal variations is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging (cite).

@@

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
in prep?).
Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
SOMECANDIDATE.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (\eqalt{linear-model}), we modeled the light curve as a linear
combination of ELCs and a simple box transit model at a given period, phase,
and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.
Since the motions won't necessarily point in a consistent direction across
transits, we treat each transit independently and report the average offset
amplitude weighted by the precision of each measurement.
To compute the significance of a centroid offset, we bootstrap the offset
amplitude for models at the same period and duration but randomly oriented
phases.
If the centroid measured for the candidate transit is substantially larger
than the random realizations, we label the candidate as a false positive.
In practice, the precision of the centroid measurements isn't sufficient to
robustly reject many candidates but two candidates---EPIC 201202105 and EPIC
201632708---have offsets large enough that we remove them from our final
catalog.
Figure SOMEFIGURE shows the distribution of centroid offsets across the full
catalog.

@@

Out of the 21,703 Campaign 1 light curves, our pipeline returns 741 signals
that pass the signal-to-noise and period cuts.
After hand vetting by the two first authors, this list is reduced to 101
convincing astrophysical transit candidates.
Of these, 38 signals---in 33 light curves---have no visible secondary
eclipse and these planet candidates are listed in \tab{cand}.
Two were previously published \citep{Crossfield:2015} but, to our knowledge,
the remaining list is currently unpublished.
The third planet published by \citet{Crossfield:2015} is found as the third
signal for that target by our pipeline but it falls just below our
signal-to-noise cut so we left it out of the catalog for consistency.
This suggests that a less conservative cut in signal-to-noise and more
aggressive machine vetting could yield a much more complete catalog at smaller
radii and longer periods even with the existing dataset.

The remaining signals are caused by eclipsing binaries.
In most cases, the search reports the secondary eclipse as a candidate and in
a few very high signal-to-noise cases, the period reported by the pipeline is
incorrect and multiple candidates correspond to the same transit.
After accounting for these by hand, we find 18 eclipsing binary candidates
and list them in \tab{eb} along with the period, phase, and depth reported by
the pipeline.
It is important to note that the choices made in the search were
heuristically tuned to find planets, not binaries, so this list should not be
considered complete or exhaustive, especially at short orbital periods.

For the planet candidates, we perform a full physical transit fit to the light
curve.
To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
sample from the posterior probability for the stellar and planetary
parameters taking limb darkening and integration time into account.
In this fit, we continue to model the trends in the data as a linear
combination of 150 ELCs but, at this point, we combine this with a realistic
light curve model \citet{ma, kipping-ld}.
Even though we have no constraints on the stellar parameters, we also sample
over a large range in stellar mass and radius so that future measurements can
be applied by re-weighting the published samples.
In \tab{cand} we list the sample quantiles for the observable quantities and
the full chains are available electronically at \dfmtodo{some URL}.

@@

\begin{table}[p]
\begin{center}
\include{tab-eb}
\end{center}
\caption{%
Probable binaries. \
$^\mathrm{a}$ The period for EPIC 201161715 was estimated using the secondary
eclipses since there is only a single primary transit.
\tablabel{eb}}
\end{table}
